RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-07-18 manuscripts/manuscript.Rmd
tweaking mansucript
Avoid running tests that may fail due to missing dependencies on certain CRAN architectures (e.g. Solaris, see NEWS)

---
#layout: preprint
layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: SimonFraser
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: SimonFraser
    address: |
      Department of Biology, Simon Fraser University, Burnaby, Canada
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML is a new phylogenetic informatics data and metadata exchange 
      format that offers substantial improvements in reliability, extensibility, 
      and richness over earlier standards such as NEXUS. In this paper we present 
      the RNeXML package which provides a bridge between this rich and reliable
      data format and the extensive library of phylogenetic tools already
      available in R, with a particular emphasis on comparative methods.

@@

```{r}
get_citation(birds)
```

```{r}
get_taxa(birds)
```

@@

This project was supported in part by a grant from the Alfred P Sloan
Foundation (CB and SC), NSF Grant DBI-1306697 (CB), ... <!-- FIXME Rutger, Hilmar, add whatever you'd like to acknowledge here -->

>>>>

---
#layout: preprint
layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: ropensci
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: ropensci
    address: |
      University of California, Berkeley, CA, USA
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML is a new phylogenetic informatics data and metadata exchange 
      format that offers substantial improvements in reliability, extensibility, 
      and richness over earlier standards such as NEXUS. In this paper we present 
      the RNeXML package which provides a bridge between this rich and reliable
      data format and the extensive library of phylogenetic tools already
      available in R, with a particular emphasis on comparative methods.

@@

```{r get_citation}
get_citation(birds)
```

```{r get_taxa}
get_taxa(birds)
```

@@

This project was supported in part by a grant from the Alfred P Sloan
Foundation Grant 2013-6-22 (CB and SC), NSF Grant DBI-1306697 (CB), ... <!-- FIXME Rutger, Hilmar, add whatever you'd like to acknowledge here -->
